---
title: "Time Series Assignment 2"
author: "Kshitij Mittal"
date: "2023-07-03"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Importing Libraries
```{r Libs}
#install.packages('tseries')
#install.packages('fpp')
#install.packages('ggplot2')
#install.packages('forecast')

library(tseries)
library(fpp)
library(ggplot2)
library(forecast)
```

For this exercise, use the Quarterly international arrivals to Australia from the US. 1981Q1 -
2012Q3 dataset. (Dataset Name: visitors.rda)
(4 points) Question 1:

## Q1

```{r Q1}
# Load the visitors.rda dataset, make a time plot of your data and describe the main features of the series

load('/Users/kshitijmittal/Documents/UChicago Acad/uchicago_codebase/08_TimeSeries/02 TS Decomposition/visitors.rda')
visitors_ts <- ts(data=visitors, frequency=4, start=c(1981,1), end = c(2012,3))
visitors_ts = visitors_ts[, "Arrivals"]
plot(visitors_ts)
```


## Q2

```{r Q2, echo=FALSE}

fit_add <- decompose(visitors_ts, type="additive")
fit_mult <- decompose(visitors_ts, type="multiplicative")

plot(fit_add)
plot(fit_mult)

```
Both Additive and Multiplicative models perform almost equally while inspecting the random noise. But for multiplicative the
variation in random is less, and we will use this model for the first round 

## Q3
Use the hw() function to forecast the next 20 quarters using Holt-Winters’ methods
```{r, figures-side, fig.show="hold", out.width="50%"}

vis_f_add <- hw(visitors_ts,seasonal = "additive",h=20)
vis_f_multi <- hw(visitors_ts,seasonal = "multiplicative",h=20)

vis_f_Damped_add <- hw(visitors_ts,seasonal = "additive",h=20, damped = TRUE)
vis_f_Damped_multi <- hw(visitors_ts,seasonal = "multiplicative",h=20, damped = TRUE)

par(mar=c(2,2,3,2))
plot(vis_f_add)
plot(vis_f_multi)
plot(vis_f_Damped_add)
plot(vis_f_Damped_multi)

```

## Q4
Use the accuracy() function to compare the Root-Mean-Square-Error (RMSE) values of the forecasts from the various methods.

```{r, Q4}
print('ADDITIVE')
accuracy(vis_f_add)

print('MULTIPLICATIVE')
accuracy(vis_f_multi)

print('ADDITIVE WITH DAMPENING')
accuracy(vis_f_Damped_add)

print('MULTIPLICATIVE WITH DAMPENING')
accuracy(vis_f_Damped_multi)

```

Multiplicative with Dampening has the least RMSE value of the 4 methods tested above


## Q5
Use the checkresiduals() function to check that the residuals from the best model look like white noise and provide a summary of the model’s smoothing parameters using the summary() function

```{r, Q5}

checkresiduals(vis_f_Damped_multi)
summary(vis_f_Damped_multi)

vis_f_Damped_multi$model
```

## Q6
Use the snaive() function to forecast the next 20 quarters, and the accuracy() function to 
evaluate the model.

```{r, Q6}

fw_snaive=snaive(visitors_ts, h=20)
accuracy(fw_snaive)

```

