---
title: "Time Series Assignment 1"
author: "Kshitij Mittal"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 1

Making the small sample

```{r small sample}
set.seed(100)

sample_q5_small=rnorm(10, mean = 2.3, sd=1.2)
small_sample_mean=mean(sample_q5_small)
small_sample_sd=sd(sample_q5_small)

```

```{r small sample distrib, echo=FALSE}
hist(sample_q5_small, col = "lightblue", main = "Distribution - Small Sample", xlab = "Value", ylab = "Frequency")
abline(v = small_sample_mean, col = "red", lwd = 2, lty = 2)  # Add vertical line for mean
abline(v = small_sample_mean - small_sample_sd, col = "blue", lwd = 2, lty = 2)  # Add vertical line for lower bound
abline(v = small_sample_mean + small_sample_sd, col = "blue", lwd = 2, lty = 2)  # Add vertical line for upper bound

```

Expanding Sample Size to 10_000

```{r big sample}
set.seed(100)

sample_q5_big=rnorm(10000, mean = 2.3, sd=1.2)
big_sample_mean=mean(sample_q5_big)
big_sample_sd=sd(sample_q5_big)

```

```{r big sample distrib, echo=FALSE}
hist(sample_q5_big, col = "lightblue", main = "Distribution - 10000 Sample", xlab = "Value", ylab = "Frequency")
abline(v = big_sample_mean, col = "red", lwd = 2, lty = 2)  # Add vertical line for mean
abline(v = big_sample_mean - big_sample_sd, col = "blue", lwd = 2, lty = 2)  # Add vertical line for lower bound
abline(v = big_sample_mean + big_sample_sd, col = "blue", lwd = 2, lty = 2)  # Add vertical line for upper bound

```

Larger samples tend to provide more accurate estimates of population parameters. Increasing the sample size from 10 to 10,000 can improve the precision of the estimated sample mean and sample standard deviation. The larger sample size allows for a better representation of the underlying distribution and reduces the impact of random fluctuations

Sample Mean and SD from sample size of 10000 would be more reliable estimates





